### 2023-05-03 paper.Rmd
after the revision its four anticlustering methods

After the five anticlustering methods and the random allocation procedure had been applied to the 10,000 data sets for $K = 2$, $K = 3$, $K = 4$, I investigated how well the competing methods were able to create similar groups. To this end, I analyzed the discrepancy in means, standard deviations, skewness and kurtosis between groups---for each data set for each $K$. To quantify the discrepancy in group means, the following computation was used: for each of the (2, 3, 4 or 5) features, all (2, 3 or 4) group means were computed. For each feature, the difference between the minimum and maximum group mean was used as a measure of discrepancy; the global discrepancy in means ($\Delta M$) was then determined as the average discrepancy across features. The same procedure was applied to compute the discrepancy in standard deviations ($\Delta \mathit{SD}$), skewness ($\Delta \mathit{Skew}$) and kurtosis ($\Delta \mathit{Kurtosis}$).

>>>>

After the four anticlustering methods and the random allocation procedure had been applied to the 10,000 data sets for $K = 2$, $K = 3$, $K = 4$, I investigated how well the competing methods were able to create similar groups. To this end, I analyzed the discrepancy in means, standard deviations, skewness and kurtosis between groups---for each data set for each $K$. To quantify the discrepancy in group means, the following computation was used: for each of the (2, 3, 4 or 5) features, all (2, 3 or 4) group means were computed. For each feature, the difference between the minimum and maximum group mean was used as a measure of discrepancy; the global discrepancy in means ($\Delta M$) was then determined as the average discrepancy across features. The same procedure was applied to compute the discrepancy in standard deviations ($\Delta \mathit{SD}$), skewness ($\Delta \mathit{Skew}$) and kurtosis ($\Delta \mathit{Kurtosis}$).
